% Modified Version of: https://github.com/sb2nov/resume, available under MIT License


\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1 } & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{ #1 }{ #2 }\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://ayan-b.github.io/}{\Large Ayan Banerjee}} & Email: \href{mailto: ayanbn7@gmail.com}{ayanbn7@gmail.com} \(|\) Mobile : +91 8016399022 \\
 \href{https://github.com/ayan-b}{GitHub} \(|\)
 \href{https://gitlab.com/ayan-b}{GitLab} \(|\) \href{https://www.linkedin.com/in/ayanb/}{LinkedIn} \(|\) \href{https://codechef.com/users/ayan_nitd}{CodeChef}%\(|\) 
 %\href{https://ayan-b.github.io/}{Personal Site}
 & Room No - 342, Hall - 1, NIT Durgapur, Durgapur - 713 209
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
  \resumeSubheading
      {\href{https://nitdgp.ac.in}{National Institute of Technology Durgapur}}{Durgapur, WB, India}
      {B.Tech in Electronics and Communication Engineering, CGPA: 9.30/10 (till 5th semester)}{2016 - 2020}
  \resumeSubheading
      {\href{http://www.rkmsargachi.org/}{Sargachi Ramakrishna Mission High School}}{Sargachi, WB, India}
      {Higher Secondary, Science, 96\%}{2014 - 2016}
  \resumeSubheading
      {\href{http://www.rkmsargachi.org/}{Sargachi Ramakrishna Mission High School}}{Sargachi, WB, India}
      {Secondary, 92.43\%}{2008 - 2014}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Indian Institute of Technology Bombay}{Mumbai, India}
    {Summer Intern at FOSSEE under Prof. Kannan Moudgalya}{May - July, 2018}
    \resumeItemListStart
      \item\small
        {Top 60 among more than 22,500 applicants.}
      \item\small
        {Integrated a plagiarism detector with Yaksh, a course taking application.}
      \item\small
        {Used Abstract Syntax Tree to obtain similarity between codes.}
      \resumeItem{Django}
        {Worked in a huge code-base written in Django.}
      \item\small
        {The feature is to be regularly used inside IIT Bombay and in Spoken Tutorial courses by thousands of students.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd
  
% ------------- PROJECTS ------------------------------- %
\section{Projects}
      \setlength{\itemsep}{0.5pt}
      \begin{itemize}
        \item\textbf{\href{https://github.com/ayan-b/GitHub-Activity-Checker}{GitHub Activity Checker}}{: A web app to show a GitHub user\textsc{\char13}s public activities, built using GitHub API, jQuery and Ajax.}\\
        % \item\textbf{Desktop Wallpaper Changer}\\
        \item\textbf{\href{https://github.com/ayan-b/Analog-Clock-Reading}{Analog Clock}}{: A 3D animated clock, built using THREEjs and WebGL.}\\
        \item\textbf{Smart Dustbin}{: Built a smart dustbin which can sense the percentage filled, built using Arduino, NodeMCU, Django, Google Sheets API; this project came first in the IoT hackathon in Aavishkar, the tech
        fest of NIT Durgapur; a team project.}\\
        \item\textbf{Open Source Contributions}
        \begin{itemize}
            \item{Contributor at coala, a language independent linter and moban, a jinja2 CLI command for static text generation.}\\
            \item\textbf{Mentor, Google Code-In}{(Oct - Dec, 2018)}{: Mentored school students to contribute in open source for coala.}
         \end{itemize}   
      \end{itemize}
  
% -------------- ACHIEVEMENTS -------------------------- %
\section{Achievements \& Responsibilities}
    \resumeItemListStart
     \setlength{\itemsep}{0.5pt}
      \item
        {Ranked \textbf{191}st among 8251 participants in \href{https://www.codechef.com/rankings/FEB18?filterBy=Institution\%3DNational\%20Institute\%20of\%20Technology\%2C\%20Durgapur&order=asc&sortBy=rank}{CodeChef} February 2018 Long Challenge.}
      \item
        {Conducted \href{https://www.hackerrank.com/dec18}{\textbf{Decathlon 2018}} \& \href{https://www.hackerrank.com/decathlon19}{\textbf{Decathlon 2019}}, the annual programming contest of the fest Aarohan.}
      \item
        {Ranked \textbf{1881}st among more than 150,000 participants in \href{https://codechef.com/users/ayan_nitd}{CodeChef} (Best Ranking, Sept, '18).}
      \item
        {Ranked \textbf{13}th among more than 750,000 candidates in state in Higher Secondary Examination
        (10+2).}
      \item
        {\textbf{Topped} from school in Secondary Examination.}
      \item
        {Awarded \textbf{NTSE Scholarship} (2012-14) by NCERT.}
    \resumeItemListEnd

% ----------------- SKILLS -------------------------------- %
\section{Skills}
 \resumeSubHeadingListStart
    \setlength{\itemsep}{1pt}
     \item\textbf{Proficient In}{: C, C++, Python, Data Structures and Algorithms, Version Control System (git), Object Oriented Programming}\\
     \item\textbf{Familiar With}{: SQL, Linux, Web Technologies (HTML, CSS, JavaScript), WebGL, Backend Technologies (Django, Flask), Machine Learning, Deep Learning, PyTorch, \LaTeX}
 \resumeSubHeadingListEnd
 
% ----------------- EXTRACURRICULAR ----------------------- %
% \section{Extracurricular Activities}
%     \resumeItemListStart
%      \setlength{\itemsep}{0.5pt}
%         \item\textbf{National Service Scheme}{ (2017-Present): Organized annual survey and medical camps in villages.}
%         \item\textbf{National Cadet Corps}{ (2011-13, 2016-17)}{: Took part in parades during Sports Day,
%         Independence Day and Republic Day.}
%     \resumeItemListEnd
% %-------------------------------------------
\end{document}
